Target Speaker Extraction using Discrete Representations from Self-Supervised Models and Language Models \thanks{Identify applicable funding agency here. If none, delete this.}

### 2024-09-06 src/paper.tex
update

\begin{table*}
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{cccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{4-6}
                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
                                    % \cline{2-2}
            \hline
            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-WavLM   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-WavLM       & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            \hline
            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
            and TSELM, we compare the speaker similarity with the discretized target speech 
            (Target-discrete-WavLM) instead of the target speech due to the observation that 
            the process of discretization already losses the speaker information (0.653 for 
            Target-discrete-WavLM). We use "\_d" to denote it.  }
            \label{main_exp}
      \end{center}
  \end{table*}

@@

\section{Results and Discussions}
Table \ref{main_exp} shows the performance of different systems on the Libri2Mix test.
The model size for Target-discrete-WavLM denotes the model size of the encoder and 
decoder, which is WavLM Large and HiFi-GAN respectively. DNSMOS is calculated over the 
test sets since it is reference-free. dWER is calculated with the clean speech instead 
of the discretized speech due to our observations that this does not make much difference. 
For TSELM-L-Hybrid and TSELM, we compute the speaker similarity with the discretized
target speech (Target-discrete-WavLM).

% instead of the target speech due to the observation that the process of discretization already losses the speaker
% information (0.653 for Target-discrete-WavLM).

>>>>

\begin{table*}
    \setlength{\tabcolsep}{12pt} % Adjust column spacing
    \renewcommand{\arraystretch}{1.3}
    \begin{center}
        \begin{tabular}{cccccccc}
            \Xhline{2\arrayrulewidth} % Bold top line
            \multirow{2}{*}{System} & \multirow{2}{*}{Model type} & \multirow{2}{*}{Model size} & \multicolumn{3}{c}{ DNSMOS $\uparrow$} & \multirow{2}{*}{dWER $\downarrow$} & \multirow{2}{*}{Spk Sim $\uparrow$} \\
            \cline{4-6}
                                    &                             &                             & SIG     & BAK     & OVL    &                       &                          \\ 
            \hline
            Mixture                 & -                           & -                           & 3.39    & 3.14    & 2.68   & 79.3\%                & -                        \\
            Target-discrete-WavLM   & -                           & 330M                           & 3.57    & 4.10    & 3.32   & 11.3\%                & 0.653                    \\
            \hline
            Spex+                   & Continuous                  & 11M                         & 3.36    & 3.76    & 2.98   & 19.3\%                & 0.923                    \\
            \hline
            Continuous-WavLM       & Continuous                  & 220M                        & 3.56    & 4.06    & 3.27   & 14.7\%                & 0.877                    \\
            TSELM-L-Hybrid          & Hybrid                      & 468M                        & 3.50    & 4.06    & 3.22   & 19.8\%                & 0.924\_d                 \\
            \hline
            TSELM-S                 & Discrete                    & 354M                        & 3.50    & 4.07    & 3.24   & 28.1\%                & 0.892\_d                 \\
            TSELM-M                 & Discrete                    & 389M                        & 3.49    & 4.05    & 3.22   & 28.4\%                & 0.901\_d                 \\
            TSELM-L                 & Discrete                    & 468M                        & 3.49    & 4.05    & 3.22   & 27.1\%                & 0.905\_d \\
            \Xhline{2\arrayrulewidth} % Bold top line              
            \end{tabular}
            \linebreak
            \caption{The performance of different systems on Libri2Mix testset. For TSELM-L-Hybrid  
            and TSELM, we compare the speaker similarity with the discretized target speech 
            (Target-discrete-WavLM) instead of the target speech due to the observation that 
            the process of discretization already losses the speaker information (0.653 for 
            Target-discrete-WavLM). We use "\_d" to denote it.  }
            \label{main_exp}
      \end{center}
  \end{table*}

@@

\section{Results and Discussions}
Table \ref{main_exp} shows the performance of different systems on the Libri2Mix test.
The model size for Target-discrete-WavLM denotes the model size of the encoder and 
decoder, which is WavLM Large and HiFi-GAN respectively. DNSMOS is calculated over the 
test sets since it is reference-free. dWER is calculated with the clean speech instead 
of the discretized speech due to our observations that this does not make much difference. 
For TSELM-L-Hybrid and TSELM, we compute the speaker similarity with the discretized
target speech (Target-discrete-WavLM) instead of the target speech.
% due to the observation that the process of discretization already losses the speaker
% information (0.653 for Target-discrete-WavLM). 
We observe that the process of discretization already losses the speaker
information (0.653 for Target-discrete-WavLM), and it might be related to the inevitable speaker 
information loss by the process of discretization. Future work should focus on developing better 
tokenization methods for SSL models. 
Since work focuses on using the discretized information 
to do target speaker extraction instead of developing better tokenization methods, we think it is 
reasonable to compare our outputs with the discretized speech since it serves as an upper bond.

We observe that our model performs better than Spex+ in terms of the DNSMOS scores but worse in dWER.
